---
title: "Reserving Ensemble"
output: html_notebook
---


 
```{r Setup, results='hide', echo=FALSE}
# NOTE remember to 'restart R and clear all outputs' if changing triangle size
# Number of triangles/simulations
n.sims <- 100
tri.size <-40
## Note: the current code only supports triangle size of 20 x 20 and 40 x 40 

source('utils/load_required_packages.R')
source('utils/defining_helper_functions.R')
source('ensemble/defining_component_functions.R')
source('ensemble/fitting_component_models.R')
source('ensemble/building_ensembles.R')
source('utils/defining_scoring_functions.R')
source('simulation/simulating_ensembles.R')
source('utils/functions_for_trisize.R')
```

# Simulations of example data

The descriptions of the simulated datasets could be found in **6.1: Example data** in the paper. 

```{r Simulation}
simulate_claims <- F

if (simulate_claims) {source('simulation/simulate_claims.R')}
```



# Fitting component models

A summary of the component models included in the ensemble could be found in **2. Choice of component models** in the paper; the details of each component model could be found in **Appendix A. Descriptions of component models** in the paper. 

```{r}
## Defining the offsets used in the non-negative distributions:
tau_Ga <- 2
tau_LN <- 2
```


```{r Fitting Component Models, results='hide'}
# Meta data format:
#   List of simulations. each simulation has:
#       Rows: number of data pints in prediction
#       Cols: number of component model + 2 (origin and dev cols)

# In-sample 
fitted_components_valid <- list()
meta_mu_valid <- list()
meta_dens_valid <- list()
meta_CDF_valid <- list()

# Out-sample
fitted_components_outsample <- list()
meta_mu_outsample <- list()
meta_dens_outsample <- list()
meta_CDF_outsample <- list()

suppressWarnings({

for (sim in 1:n.sims) {
    # Train on train, test on valid-test
    past_data <- read.csv(sprintf('simulation/triangle_%s-data/sim%s-past-data.csv', tri.size, sim))
    past_data_split <- claims_df_train_val_test(past_data)
    results_past <- fit_all_component_models(past_data_split$train, past_data_split$valid) 
    
    # Train on train+valid, test on test
    full_data <- read.csv(sprintf('simulation/triangle_%s-data/sim%s-full-data.csv', tri.size, sim))
    full_data_split <- claims_df_in_out(full_data)
    results_full <- fit_all_component_models(rbind(full_data_split$train, full_data_split$valid), full_data_split$test)
    
    fitted_components_valid[[sim]] <- results_past$component_models
    meta_mu_valid[[sim]] <- results_past$meta_mu
    meta_dens_valid[[sim]] <- results_past$meta_dens
    meta_CDF_valid[[sim]] <- results_past$meta_CDF
    fitted_components_outsample[[sim]] <- results_full$component_models
    meta_mu_outsample[[sim]] <- results_full$meta_mu
    meta_dens_outsample[[sim]] <- results_full$meta_dens
    meta_CDF_outsample[[sim]] <- results_full$meta_CDF
    
    if (floor(sim %% (n.sims/4)) == 0) {
        print(sprintf('... Completed %s of %s simulations...', sim, n.sims))
    }
}
    
})
```


# Fitting Benchmark Models

This section fits the benchmark models described in **3.2: Best Model in the Validation set (BMV)** and **3.3: Equally Weighted ensemble (EW)** in the paper. 

```{r Fitting Benchmark Models}
best_model_val_index <- c()
if(tri.size == 40){
    n.models <- 18
} else{
    n.models <- 16
}

# Equally Weighted Ensemble
w_init_1_3<-rep(1/n.models,n.models)

for (sim in 1:n.sims) {
    #Calculate Best Performance Model in the validation set
    LogS_valid_IndEn2 <- log(meta_dens_valid[[sim]][, -c(1, 2)] + 1e-6)
    best_model_val_index[sim] <- which.max(apply(LogS_valid_IndEn2, MARGIN=2, FUN=mean))
}

names(best_model_val_index) <- names(fitted_components_valid[[1]])[best_model_val_index]
```

# Fitting Ensemble Models:

This section fits the SLP and ADLP ensembles described in **3.4. Standard linear pool ensembles (SLP)** and **3.5. Accident and Development period adjusted Linear Pools (ADLP) driven by general insurance characteristics** in the paper. 

```{r Fitting Ensemble Models}
# all_ensemble format
#     List of ensemble models (each fit on its own partition). Each model has:
#         - Out-of-sample density
#             - number of simulations
#                 - value for each partition
#         - Out-of-sample CDF
#             - number of simulations
#                 - value for each partition
#         - Final model weights for each component
#             - number of simulations
#                 - value for each partition
#         - List of partitions
#             - Each item in the list is the indices used in partition
#         - optimMM object from the MM optimisation
#     

all_ensembles <- fit_all_partition_ensembles(
    meta_dens_valid, 
    meta_dens_outsample
)

EW <- list(
    model_weights_simul_sims = weights_for_EW_all_sims(n.sims, w_init_1_3),
    partition_func = par0,
    optimMM = NULL
)

BMV <- list(
    model_weights_simul_sims = weights_for_BMV_all_sims(n.models, best_model_val_index),
    partition_func = par0,
    optimMM = NULL
)

all_ensembles$EW <- EW
all_ensembles$BMV <- BMV

EW_ind <- length(all_ensembles) - 1
BMV_ind <- length(all_ensembles)

n.ensembles <- length(all_ensembles)
```

# Goodness of Fit Measures

This section calculates and presents the Log Score and CRPS results of the fitted ensembles as shown in **6.2.1. SLP: the Standard Linear Pool ensemble**, **6.2.2. ADLP1 to ADLP18: Linear Pool ensembles with different data partition strategies** and **6.3. Comparisons using the CRPS** in the paper.

```{r Calculate logS for each new observation y_k}
# Level of Data within list
# - Ensemble
# - Simulation
# - Data

component_logS <- lapply(
    meta_dens_outsample, FUN = function(x) log(x[, -c(1, 2)] + 1e-6)
)

ensemble_dens <- calc_dens_ensemble(meta_dens_outsample, all_ensembles)
ensemble_logS <- lapply(
    ensemble_dens, FUN = function(x) lapply(x, FUN = function(y) log(y+1e-6))
)
names(ensemble_logS) <- names(all_ensembles)

```

```{r Calculate CRPS for each new observation y_k}
suppressWarnings({

ensemble_CRPS <- calc_crps_ensemble(
    n.sims, 
    fitted_components_outsample, 
    all_ensembles
)

})

#CRPS_comparision_ADLP <- unlist(lapply(ensemble_CRPS, FUN = function(x) mean(unlist(x))))[1:(n.ensembles-2)]
#CRPS_comparision_ADLP <- unlist(lapply(ensemble_CRPS, FUN = function(x) median(unlist(x))))[1:(n.ensembles-2)]
```

```{r}
CRPS_comparision_ADLP <- unlist(lapply(ensemble_CRPS, FUN = function(x) mean(unlist(x))))[1:(n.ensembles-2)]
```


```{r Exploratory Data Analysis - Checking NA densities}
## NA exploration:

na.SLP <- c()
for(i in 1:n.sims){
   na.SLP[i] <- sum(is.na(ensemble_logS[[1]][[i]]))
}


apply(meta_dens_outsample[[which.max(na.SLP)]], FUN = function(x) sum(is.na(x)==TRUE), MARGIN = 2)

```


```{r Exploratory Data Analysis - Log Score Plots}


# Log Score Boxplots

mean_score_over_sim <- lapply(ensemble_logS, FUN = function(x) unlist(lapply(x, FUN = function(y) mean(y))))

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_LogScoreBoxPlot.pdf"))
ggplot(data=stack(data.frame(mean_score_over_sim)[, c('ADLP_par0', 'BMV', 'EW')]), aes(x = ind, y = values)) + 
    geom_boxplot()+labs(x="Model",y="Log Score") +
    ggtitle(paste("Average Log Score", "with Tau =", tau_Ga)) +
    scale_x_discrete(labels=c('SLP','BMV', 'EW'))
#dev.off()

# Log Score with Different Split Points
corres_splitpoints_SLPincluded<-c(0, split_points)
LS_comparision_ADLP <- unlist(lapply(ensemble_logS, FUN = function(x) mean(unlist(x), na.rm = TRUE)))[1:(n.ensembles-2)]
#LS_comparision_ADLP <- unlist(lapply(ensemble_logS, FUN = function(x) median(unlist(x))))[1:(n.ensembles-2)]

optim_ADLP_index <- which.max(LS_comparision_ADLP)
optim_ADLP_splitPoint <- corres_splitpoints_SLPincluded[optim_ADLP_index]

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_MeanLogScorebySplitPoints.pdf"))
#par(mar = c(3.8, 3.8, 3.8, 2))
plot(x=corres_splitpoints_SLPincluded, y=LS_comparision_ADLP,
     type="p",xlab="Accident Periods",ylab="Mean Log Score",
     main="Mean Log Score v.s. Different split points")
points(x=corres_splitpoints_SLPincluded[which.max(LS_comparision_ADLP)], y=max(LS_comparision_ADLP),
       type="p",col="black",pch=16,cex=1.6)
points(x=0,y=LS_comparision_ADLP[1],type="p",col="grey",pch=16,cex=ifelse(which.max(LS_comparision_ADLP) == 1, 0.8, 1.6))
legend('topleft' ,legend=c("SLP","Optimal ADLP"),col=c("grey","black"),pch=c(16,16),cex=1)
#dev.off()

# Log Score by Accident Periods
out_sample_ap <- meta_dens_outsample[[1]]$origin
all_ap <- sort(unique(out_sample_ap))
LS_AP_components <- average_by_index_sim(out_sample_ap, component_logS)
LS_AP_ensembles <- lapply(ensemble_logS, FUN = function(x) average_by_index(out_sample_ap, x))

# Log Score by Accident periods: Component models

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_LogScorebyAccidentPeriodsSLP.pdf"))
#par(mar = c(3.8, 3.8, 3.8, 0))
model_names <- colnames(meta_dens_outsample[[1]])[3:(n.models + 2)]
plot(x=all_ap,y=LS_AP_components[[1]],
     col="grey",ylim=c(-8,0),type="l",main="Log-Score by Accident Periods ",ylab="Mean Log Score",xlab="Accident Periods")
for (i in 2:length(LS_AP_components)){
  points(x=all_ap,y=LS_AP_components[[i]],col="grey",type="l")
}

points(x=all_ap, y=LS_AP_components[[which(model_names == "dens_PPCF")]],col="orange",type="l",lwd=1)
points(x=all_ap, y=LS_AP_components[[which(model_names == "dens_ZAGA")]],col="brown",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[BMV_ind]],col="green",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[1]],col="yellow",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[EW_ind]],col="red",type="l",lwd=1)

legend('topright',
       legend=c("Component Models",
                "PPCF",
                "ZAGA",
                "Best Models in Validation Set",
                "SLP", "Equally Weighted Ensemble"),
       col=c("grey", "orange","brown","green","yellow","red"),lty=1,cex=0.6)
#dev.off()

# Log Score by Accident periods: ADLP ensembles
#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_LogScorebyAccidentPeriodsADLP.pdf"))
#par(mar = c(3.8, 3.8, 3.8, 0))
plot(x=all_ap,y=LS_AP_components[[1]],
     col="grey",ylim=c(-8,0),type="l",main=paste("Log-Score by Accident Periods", "with Tau=", tau_Ga),ylab="Mean Log Score",xlab="Accident Periods")
for (i in 2:length(LS_AP_components)){
  points(x=all_ap,y=LS_AP_components[[i]],col="grey",type="l")
}
#points(x=all_ap,y=LS_AP_components[[12]],col="brown",type="l")

points(x=all_ap,y=LS_AP_ensembles[[1]],col="yellow",type="l",lwd=2)
points(x=all_ap,y=LS_AP_ensembles[[2]],col="#2417DA",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[optim_ADLP_index]],col="#6D4691",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[length(split_points) + 1]],col="#FFA500",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[EW_ind]],col="red",type="l",lwd=1)
points(x=all_ap,y=LS_AP_ensembles[[BMV_ind]],col="green",type="l",lwd=1)
legend('topright',
       legend=c("Component Models",
                "Best Models in Validation Set",
                "SLP","ADLP 1(AP 2-3)",paste0("ADLP", " ", optim_ADLP_index-1, "(AP2-", optim_ADLP_splitPoint,")"), "ADLP 18(AP2-33)","Equally Weighted Ensemble"),
       col=c("grey","green","yellow","#2417DA","#6D4691","#FFA500","red"),lty=1,cex=0.6)
#dev.off()
```




```{r Exploratory Data Analysis - CRPS Plots}


# CRPS Boxplots
print("Warnings: the following plots are only available for Triangle size 40 (i.e., the main results in the paper)")
mean_score_over_sim <- lapply(ensemble_CRPS, FUN = function(x) unlist(lapply(x, FUN = function(y) mean(y))))

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_CRPSBoxPlot.pdf"))

ggplot(data=stack(data.frame(mean_score_over_sim)[, c('ADLP_par0', 'ADLP_par12','ADLP_par8', 'BMV', 'EW')]), aes(x = ind, y = values)) + 
    ylim(12, 22) +
    geom_boxplot()+labs(x="Model",y="CRPS") +
    ggtitle(paste("Average CRPS", "with Tau =", tau_Ga)) +
    scale_x_discrete(labels=c('SLP','ADLP 12','ADLP 8','BMV', 'EW'))

#dev.off()

# CRPS with Different Split Points
corres_splitpoints_SLPincluded<-c(0, split_points)

#par(mar = c(3.8, 3.8, 3.8, 2))
#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_CRPSbySplitpoints.pdf"))

plot(x=corres_splitpoints_SLPincluded, y=CRPS_comparision_ADLP,
     type="p",xlab="Accident Periods",ylab="Mean CRPS",
     main=paste("Mean CRPS v.s. Different split points", "with Tau = ", tau_Ga))
points(x=corres_splitpoints_SLPincluded[which.min(CRPS_comparision_ADLP)], y=min(CRPS_comparision_ADLP),
       type="p",col="black",pch=16,cex=1.6)

points(x=corres_splitpoints_SLPincluded[optim_ADLP_index], y=CRPS_comparision_ADLP[optim_ADLP_index],
      type="p",col="brown",pch=16,cex=1.6)

points(x=0,y=CRPS_comparision_ADLP[1],type="p",col="grey",pch=16,cex=ifelse(which.min(CRPS_comparision_ADLP) == 1, 0.8, 1.6))
legend('bottomleft' ,legend=c("SLP","ADLP 8", "ADLP 12"),col=c("grey","black", "brown"),pch=c(16,16),cex=1)

#dev.off()

# CRPS by Accident Periods
ensemble_all_ap <- lapply(ensemble_CRPS, function(y) as.numeric(sapply(strsplit(names(y[[1]]), "-"), function(x) x[[1]])))
all_ap <- sort(unique(ensemble_all_ap[[1]]))
CRPS_AP_ensembles <- mapply(FUN = function(crps, ap_ind) average_by_index(ap_ind, crps), ensemble_CRPS, ensemble_all_ap)

#par(mar = c(3.8, 3.8, 3.8, 0))

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_CRPS_byAccidentPeriods.pdf"))

plot(x=all_ap,y=CRPS_AP_ensembles[, 1], ylim = c(2, 30),
     col="yellow",type="l",main="CRPS by Accident Periods ",ylab="Mean CRPS",xlab="Accident Periods")
points(x=all_ap,y=CRPS_AP_ensembles[, 2],col="#2417DA",type="l",lwd=1)
points(x=all_ap,y=CRPS_AP_ensembles[, optim_ADLP_index],col="#6D4691",type="l",lwd=1)
points(x=all_ap,y=CRPS_AP_ensembles[, which.min(CRPS_comparision_ADLP)],col="#FFA500",type="l",lwd=1)
points(x=all_ap,y=CRPS_AP_ensembles[, EW_ind],col="red",type="l",lwd=1)
points(x=all_ap,y=CRPS_AP_ensembles[, BMV_ind],col="green",type="l",lwd=1)
legend('topleft',
       legend=c("SLP",
                "Best Models in Validation Set",
                "ADLP 1(AP 2-3)","ADLP 12(AP2-18)","ADLP 8(AP2-14)",
                "Equally Weighted Ensemble"),
       col=c("yellow","green","#2417DA","#6D4691","#FFA500","red"),lty=1,cex=0.6)
#dev.off()
```
```{r}
## Summary of mean CRPS:
apply(data.frame(mean_score_over_sim)[, c('ADLP_par0', 'ADLP_par12','ADLP_par8', 'BMV', 'EW')], FUN = mean, MARGIN = 2)
```


# Statistical Tests of GoF Measures

This section generates the statistical test results for Log Score and CRPS as shown in **6.2.3. Analysing the difference in distributional forecast performance using statistical tests** and **6.3. Comparisons using the CRPS** in the paper. 

```{r}
optim_ADLP_index_CRPS <- which.min(CRPS_comparision_ADLP)
```

```{r Calc DM and Adj. DM Test Scores}
# names(all_ensembles)
# EW ensemble is index 20
# BMV ensemble is index 21

## Note: here we calculate both DM test statistics and adjusted DM test statistics; however, the readers are recommended using only the DM test statistics to assess model performance, as the adjusted DM test is specifically designed to account for temporal dependence in the time-series forecasting applications, which might not be applicable in the loss reserving case 

SLP_ind <- 1

DM_LS_SLPvsEW <- calc_DM_test_models(ensemble_logS, SLP_ind, EW_ind)
DM_LS_SLPvsBMV <- calc_DM_test_models(ensemble_logS, SLP_ind, BMV_ind)
ADM_LS_SLPvsEW <- calc_adj_DM_test_models(ensemble_logS, SLP_ind, EW_ind)
ADM_LS_SLPvsBMV <- calc_adj_DM_test_models(ensemble_logS, SLP_ind, BMV_ind)

DM_LS_ADLPvsEW <- calc_DM_test_models(ensemble_logS, optim_ADLP_index, EW_ind)
DM_LS_ADLPvsBMV <- calc_DM_test_models(ensemble_logS, optim_ADLP_index, BMV_ind)
ADM_LS_ADLPvsEW <- calc_adj_DM_test_models(ensemble_logS, optim_ADLP_index, EW_ind)
ADM_LS_ADLPvsBMV <- calc_adj_DM_test_models(ensemble_logS, optim_ADLP_index, BMV_ind)


DM_LS_ADLPvsSLP <- calc_DM_test_models(ensemble_logS, optim_ADLP_index, SLP_ind)
ADM_LS_ADLPvsSLP <- calc_adj_DM_test_models(ensemble_logS, optim_ADLP_index, SLP_ind)



DM_CRPS_ADLPvsEW <- calc_DM_test_models(ensemble_CRPS, optim_ADLP_index, EW_ind)

DM_CRPS_ADLPvsBMV <- calc_DM_test_models(ensemble_CRPS, optim_ADLP_index, BMV_ind)
DM_optimCRPS_ADLPvsBMV <- calc_DM_test_models(ensemble_CRPS, optim_ADLP_index_CRPS, BMV_ind)
ADM_CRPS_ADLPvsEW <- calc_adj_DM_test_models(ensemble_CRPS, optim_ADLP_index, EW_ind)
ADM_CRPS_ADLPvsBMV <- calc_adj_DM_test_models(ensemble_CRPS, optim_ADLP_index, BMV_ind)

DM_CRPS_ADLPvsSLP <- calc_DM_test_models(ensemble_CRPS, optim_ADLP_index, SLP_ind)
ADM_CRPS_ADLPvsSLP <- calc_adj_DM_test_models(ensemble_CRPS, optim_ADLP_index, SLP_ind)

DM_CRPS_ADLPvsADLP <- calc_DM_test_models(ensemble_CRPS, which.min(CRPS_comparision_ADLP), optim_ADLP_index)
ADM_CRPS_ADLPvsADLP <- calc_adj_DM_test_models(ensemble_CRPS, which.min(CRPS_comparision_ADLP), optim_ADLP_index)

```


```{r Calc DM and Adj. DM Test Statistics}
## Analysing Log Score test statistics: 
print("Log Score DM test: SLP vs EW")
mean(DM_LS_SLPvsEW > qnorm(0.975))
print("Log Score DM test: SLP vs BMV")
mean(DM_LS_SLPvsBMV > qnorm(0.975))
print("Log Score DM test: ADLP vs SLP")
mean(DM_LS_ADLPvsSLP > qnorm(0.975))

print("Log Score DM test: ADLP vs EW")
mean(DM_LS_ADLPvsEW > qnorm(0.975))
print("Log Score DM test: ADLP vs BMV")
mean(DM_LS_ADLPvsBMV > qnorm(0.975))

## Analysing CRPS test statistics: 
print("CRPS DM test: ADLP vs EW")
mean(-DM_CRPS_ADLPvsEW > qnorm(0.975))
print("CRPS DM test: ADLP vs BMV")
mean(-DM_CRPS_ADLPvsBMV > qnorm(0.975))
mean(-DM_optimCRPS_ADLPvsBMV> qnorm(0.975))
print("CRPS DM test: ADLP vs SLP")
mean(-DM_CRPS_ADLPvsSLP > qnorm(0.975))

```


```{r Graphical Results: Log Scores}

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsSLPvsBMVandEW.pdf"))

TestStats_BMV_EW <- data.frame(
    DM_EW=DM_LS_SLPvsEW,
    DM_BMV=DM_LS_SLPvsBMV
)

ggplot(data=stack(as.data.frame(TestStats_BMV_EW)),aes(x=ind,y=values)) +
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") + 
    ggtitle("Distribution of DM Statistics (SLP v.s EW & BMV)") + 
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) + 
    scale_x_discrete(labels=c('SLP v.s EW(DM)', 'SLP v.s BMV(DM)')) + 
    geom_hline(yintercept=0,linetype="dashed", color = "blue", linewidth=1)

#dev.off()

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsADLPvsBMVandEW.pdf"))

TestStats_ADLP_BMV_EW <- data.frame(
    DM_EW=DM_LS_ADLPvsEW,
    DM_BMV=DM_LS_ADLPvsBMV
)

ggplot(data=stack(as.data.frame(TestStats_ADLP_BMV_EW )),aes(x=ind,y=values)) + 
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of DM Statistics (Optimal ADLP v.s EW & BMV)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('ADLP v.s EW(DM)','ADLP v.s BMV(DM)')) +
    geom_hline(yintercept=0,linetype="dashed", color = "blue", linewidth=1)

#dev.off()



TestStats_ADLP_SLP <- data.frame(
    DM_EW=DM_LS_ADLPvsSLP
)

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsSLPvsADLP.pdf"))

ggplot(data=stack(as.data.frame(TestStats_ADLP_SLP )),aes(x=ind,y=values)) +
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of DM Statistics (Optimal ADLP v.s SLP)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('ADLP v.s SLP(DM)')) +
    geom_hline(yintercept=0,linetype="dashed", color = "blue", linewidth=1)

#dev.off()

```


```{r}
### Calculate the p-value of the test (Log Score):
p_DM_LS_SLPvsEW <- ifelse((1-pnorm(DM_LS_SLPvsEW, 0, 1))<=0.5,2*(1-pnorm(DM_LS_SLPvsEW, 0, 1)), 2*pnorm(DM_LS_SLPvsEW, 0, 1))

p_DM_LS_SLPvsBMV <- ifelse(1-pnorm(DM_LS_SLPvsBMV, 0, 1)<=0.5, 2*(1-pnorm(DM_LS_SLPvsBMV, 0, 1)), 2*(pnorm(DM_LS_SLPvsBMV, 0, 1)))

p_DM_LS_ADLPvsEW <- ifelse(1-pnorm(DM_LS_ADLPvsEW, 0, 1)<=0.5, 2*(1-pnorm(DM_LS_ADLPvsEW, 0, 1)), 2*pnorm(DM_LS_ADLPvsEW, 0, 1))

p_DM_LS_ADLPvsBMV <- ifelse(1-pnorm(DM_LS_ADLPvsBMV, 0, 1)<=0.5, 2*(1-pnorm(DM_LS_ADLPvsBMV, 0, 1)), 2*pnorm(DM_LS_ADLPvsBMV, 0, 1))

p_DM_LS_ADLPvsSLP <- ifelse(1-pnorm(DM_LS_ADLPvsSLP, 0, 1)<=0.5,2*(1-pnorm(DM_LS_ADLPvsSLP, 0, 1)),2*pnorm(DM_LS_ADLPvsSLP, 0, 1))

## Plot the box-plot :
TestStats_p_val_SLP <- data.frame(p_DM_EW=p_DM_LS_SLPvsEW,
                               p_DM_BMV=p_DM_LS_SLPvsBMV)

TestStats_p_val_ADLP <- data.frame(p_DM_EW = p_DM_LS_ADLPvsEW,
                               p_DM_BMV = p_DM_LS_ADLPvsBMV,
                               p_DM_SLP = p_DM_LS_ADLPvsSLP)

#pdf(paste0("simulation/triangle_", tri.size, "-data/TestStats_p_val_SLP.pdf"))
ggplot(data=stack(as.data.frame(TestStats_p_val_SLP)),aes(x=ind,y=values))+geom_boxplot()+labs(x="Hypothesis tests",y="p-values")+ggtitle("Distribution of Log-score p-values (SLP v.s EW & BMV)")+geom_hline(yintercept=0.05,linetype="dashed", color = "red", linewidth=1)+scale_x_discrete(labels=c('SLP v.s EW(DM)','SLP v.s BMV(DM)'))+geom_hline(yintercept=0.1,linetype="dashed", color = "blue", linewidth=1)
#dev.off()


#pdf(paste0("simulation/triangle_", tri.size, "-data/TestStats_p_val_ADLP.pdf"))

ggplot(data=stack(as.data.frame(TestStats_p_val_ADLP)),aes(x=ind,y=values))+geom_boxplot()+labs(x="Hypothesis tests",y="p-values")+ggtitle("Distribution of Log-score p-values (ADLP v.s EW, BMV & SLP)")+geom_hline(yintercept=0.05,linetype="dashed", color = "red", linewidth=1)+scale_x_discrete(labels=c('ADLP v.s EW(DM)','ADLP v.s BMV(DM)', 'ADLP v.s SLP(DM)'))+geom_hline(yintercept=0.1,linetype="dashed", color = "blue", linewidth=1)

#dev.off()




```



```{r Graphical Results: CRPS}}

## Statistical test results: CRPS 

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsOptimADLPvsBMV_CRPS.pdf"))

TestStats_OptimADLP_BMV <- data.frame(
    DM_BMV=-DM_CRPS_ADLPvsBMV
)

ggplot(data=stack(as.data.frame(TestStats_OptimADLP_BMV)),aes(x=ind,y=values)) + 
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of DM Statistics; CRPS (Optimal ADLP v.s BMV)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('Optimal ADLP v.s BMV(DM)'))

#dev.off()


#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsOptimADLPvsEW_CRPS.pdf"))

TestStats_OptimADLP_EW <- data.frame(
    DM_EW=-DM_CRPS_ADLPvsEW
)

ggplot(data=stack(as.data.frame(TestStats_OptimADLP_EW)),aes(x=ind,y=values)) +
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of DM Statistics; CRPS (Optimal ADLP v.s EW)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('Optimal ADLP v.s EW(DM)'))

#dev.off()

TestStats_OptimADLP_SLP <- data.frame(
    DM_SLP=-DM_CRPS_ADLPvsSLP
)

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsOptimADLPvsSLP_CRPS.pdf"))

ggplot(data=stack(as.data.frame(TestStats_OptimADLP_SLP)),aes(x=ind,y=values)) +
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of DM Statistics; CRPS (Optimal ADLP v.s SLP)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('Optimal ADLP v.s SLP(DM)'))

#dev.off()


TestStats_OptimADLP_ADLP <- data.frame(
    DM_ADLP=-DM_CRPS_ADLPvsADLP
)

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_testStatisticsOptimADLPvsADLP_CRPS.pdf"))

ggplot(data=stack(as.data.frame(TestStats_OptimADLP_ADLP)),aes(x=ind,y=values)) +
    geom_boxplot() +
    labs(x="Hypothesis tests",y="Test statistics") +
    ggtitle("Distribution of CRPS DM Statistics; CRPS (ADLP 12 v.s ADLP 8)") +
    geom_hline(yintercept=qnorm(0.975),linetype="dashed", color = "red", linewidth=2) +
    scale_x_discrete(labels=c('ADLP 12 v.s ADLP 8(DM)'))

#dev.off()





```


```{r}
### Calculate the p-value of the test (CRPS):

p_DM_CRPS_ADLPvsEW <- ifelse(1-pnorm(DM_CRPS_ADLPvsEW, 0, 1)<=0.5, 2*(1-pnorm(DM_CRPS_ADLPvsEW, 0, 1)), 2*pnorm(DM_CRPS_ADLPvsEW, 0, 1))

p_DM_CRPS_ADLPvsBMV <- ifelse(1-pnorm(DM_CRPS_ADLPvsBMV, 0, 1)<=0.5, 2*(1-pnorm(DM_CRPS_ADLPvsBMV, 0, 1)), 2*pnorm(DM_CRPS_ADLPvsBMV, 0, 1))

p_DM_CRPS_ADLPvsSLP <- ifelse(1-pnorm(DM_CRPS_ADLPvsSLP, 0, 1)<=0.5,2*(1-pnorm(DM_CRPS_ADLPvsSLP, 0, 1)),2*pnorm(DM_CRPS_ADLPvsSLP, 0, 1))

p_DM_CRPS_ADLPvsADLP <- ifelse(1-pnorm(DM_CRPS_ADLPvsADLP, 0, 1)<=0.5,2*(1-pnorm(DM_CRPS_ADLPvsADLP, 0, 1)),2*pnorm(DM_CRPS_ADLPvsADLP, 0, 1))



## Plot the box-plot :

TestStats_p_val_ADLP_CRPS <- data.frame(p_DM_EW = p_DM_CRPS_ADLPvsEW,
                               p_DM_BMV = p_DM_CRPS_ADLPvsBMV,
                               p_DM_SLP = p_DM_CRPS_ADLPvsSLP,
                               p_DM_ADLP = p_DM_CRPS_ADLPvsADLP)



#pdf(paste0("simulation/triangle_", tri.size, "-data/TestStats_p_val_ADLP.pdf"))

ggplot(data=stack(as.data.frame(TestStats_p_val_ADLP_CRPS)),aes(x=ind,y=values))+geom_boxplot()+labs(x="Hypothesis tests",y="p-values")+ggtitle("Distribution of CPRS p-values (ADLP v.s EW, BMV and SLP)")+geom_hline(yintercept=0.05,linetype="dashed", color = "red", linewidth=1)+scale_x_discrete(labels=c('ADLP v.s EW(DM)','ADLP v.s BMV(DM)', 'ADLP v.s SLP(DM)', 'ADLP 12 v.s ADLP 8'))+geom_hline(yintercept=0.1,linetype="dashed", color = "blue", linewidth=1)

#dev.off()




```


# Predictive performance on aggregate reserve level

This section calculates and presents the results in **6.4. Predictive performance on aggregate reserve level** in the paper. 

```{r Calculate Predicted Reserves}
central_reserve_estimate <- matrix(NA, n.sims, n.ensembles)

for (sim in 1:n.sims) {
    meta_mu <- meta_mu_outsample[[sim]]
    
    for (i in 1:n.ensembles){
        ensemble <- all_ensembles[[i]]
        meta_mu_partitions <- ensemble$partition_func(meta_mu)
        n.partitions <- length(meta_mu_partitions)
        ensemble_w <- ensemble$model_weights_simul_sims[[sim]]
        ensemble_reserve <- c()
        
        for (j in 1:n.partitions) {

            meta_partition <- meta_mu_partitions[[j]][, -c(1, 2)]
          
            mu_predict <- as.matrix(meta_partition) %*% ensemble_w[[j]]
            ensemble_reserve <- rbind(ensemble_reserve, mu_predict) 
        }
        
        central_reserve_estimate[sim, i] <- apply(ensemble_reserve,MARGIN=2,FUN=sum)
    }
}

colnames(central_reserve_estimate) <- names(all_ensembles)

```


```{r Simulating Reserves}
source('simulation/simulating_ensembles.R')

if (T) {
  
    total_reserve_simulations = 1000
    
    set.seed(100)
    
    suppressWarnings({
    all_reserve_simulations = simulate_reserves(
        n.sims, 
        total_reserve_simulations, 
        fitted_components_outsample, 
        all_ensembles
    )
    })

    all_simulations <- matrix(NA, nrow = n.sims * total_reserve_simulations,ncol = n.ensembles+2)
    for (i in 1:n.ensembles) {
        all_simulations[, i+2] <- all_reserve_simulations[[i]]
    }
    
    # Triangle
    all_simulations[, 1] <- rep(1:n.sims, each = total_reserve_simulations)
    # Simulation
    all_simulations[, 2] <- rep(1:total_reserve_simulations, n.sims)
    colnames(all_simulations) <- c('Triangle #', 'Simulation #', names(all_ensembles))
    
    write.csv(all_simulations, sprintf("simulation/empircal_simulations_ensembles-%s.csv", tri.size), row.names = FALSE)
}

simulated_reserves <- read.csv(sprintf("simulation/empircal_simulations_ensembles-%s.csv", tri.size), row.names=NULL)
```


```{r Calculate Reserve Bias}
true_reserves <- c()
# Calculate true reserves
for (sim in 1:n.sims){
    full_data <- read.csv(sprintf('simulation/triangle_%s-data/sim%s-full-data.csv', tri.size, sim))
    true_reserves <- c(true_reserves, sum(claims_df_in_out(full_data)$test[, 'aggregate_claims']))
}

## Use Median as it is more stable: 
relative_diff_centralBias <- (central_reserve_estimate-true_reserves)/true_reserves
central_reserve_bias <- apply(abs(relative_diff_centralBias), 2, median)


# 75th Quantile

quantile_reserve <- quantile(true_reserves, 0.75)
quantile_reserve_estimate <- matrix(NA, nrow = n.sims, ncol = ncol(simulated_reserves) - 2)
for (i in 1:n.sims) {
    sim_reserve <- simulated_reserves[simulated_reserves$Triangle.. == i, -c(1, 2)]
    quantile_reserve_estimate[i, ] <- apply(sim_reserve, MARGIN = 2, FUN = function(x) quantile(x, 0.75)) / 10000
}
colnames(quantile_reserve_estimate) <- colnames(simulated_reserves[, -c(1, 2)])
relative_diff_75Bias <- (quantile_reserve_estimate - quantile_reserve)/quantile_reserve
reserve_bias_75Quantile <- apply(abs(relative_diff_75Bias), MARGIN = 2, median)




```




## Graphical Results of Aggregate Reserve Bias

```{r Exploratory Data Analysis - Reserve Bias Plots}


# Reserve Bias
corres_splitpoints_SLPincluded<-c(0, split_points)

# Central Reserve
#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_CentralRelativeReserveBias.pdf"))



mean_reserve_bias <- abs(central_reserve_bias)

par(mar = c(3.8, 3.8, 3.8, 2))
plot(x=corres_splitpoints_SLPincluded, y=mean_reserve_bias[-c(EW_ind, BMV_ind)],
     type="p",xlab="Accident Periods",ylab="Mean Aggregate Reserve Bias",
     main="Mean Absolute Central Reserve Bias v.s. Different split points",
     ylim = c(0, max(mean_reserve_bias)))
points(x=corres_splitpoints_SLPincluded[optim_ADLP_index], y=mean_reserve_bias[optim_ADLP_index],
       type="p",col="black",pch=16,cex=1.6)

points(x=0,y=mean_reserve_bias[1],type="p",col="grey",pch=16,cex=ifelse(which.min(mean_reserve_bias[-c(EW_ind, BMV_ind)]) == 1, 0.8, 1.6))
legend('bottomright' ,legend=c("SLP","ADLP 12"),col=c("grey","black"),pch=c(16,16),cex=1)
abline(h = mean_reserve_bias[EW_ind], col = 'red')
abline(h = mean_reserve_bias[BMV_ind], col = 'green')
  
#dev.off()

# 75th Quantile Reserve

par(mar = c(3.8, 3.8, 3.8, 2))

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_RelativeReserveBiasat75Quantile.pdf"))


plot(x=corres_splitpoints_SLPincluded, y=reserve_bias_75Quantile[-c(EW_ind, BMV_ind)],
     type="p",xlab="Accident Periods",ylab="Absolute aggregate Reserve Bias at 75th Quantile",
     main="Absolute aggregate Reserve Bias at 75th Quantile v.s. Different split points",
     ylim = c(0, max(reserve_bias_75Quantile)))
points(x=corres_splitpoints_SLPincluded[optim_ADLP_index], y=reserve_bias_75Quantile[optim_ADLP_index ],
       type="p",col="black",pch=16,cex=1.6)

points(x=0,y=reserve_bias_75Quantile[1],type="p",col="grey",pch=16,cex=ifelse(which.min(reserve_bias_75Quantile [-c(EW_ind, BMV_ind)]) == 1, 0.8, 1.6))
legend('bottomright' ,legend=c("SLP","ADLP 12"),col=c("grey","black"),pch=c(16,16),cex=1)
abline(h = reserve_bias_75Quantile [EW_ind], col = 'red')
abline(h = reserve_bias_75Quantile [BMV_ind], col = 'green')

#dev.off()

```

```{r}
# Define the names of all the strategies used in the paper: 
all_ensembles_names <- c()
for(i in 1:19){
    all_ensembles_names[i] <- paste("ADLP", i-1)
}
all_ensembles_names[20] <- "EW"
all_ensembles_names[21] <- "BMV"


## Plot the box plot of the reserve bias: 

### Plot the box-plot of central relative reserve bias: 

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_BoxplotRelativeCentralReserveBias.pdf"))


ggplot(data=stack(as.data.frame(relative_diff_centralBias[, c("ADLP_par0", "ADLP_par12", "EW", "BMV")])),aes(x=ind,y=values))+geom_boxplot()+labs(x="Models",y="Relative reserve bias")+ggtitle("Distribution of central relative reserve bias")+ylim(-0.4, 0.8)+scale_x_discrete(labels = c("SLP", "ADLP 12", "EW", "BMV"), guide = guide_axis(angle = 45))

#dev.off()

### Plot the box-plot of 75th quantile relative reserve bias: 

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_BoxplotRelative75QuantileReserveBias.pdf"))


ggplot(data=stack(as.data.frame(relative_diff_75Bias[, c("ADLP_par0", "ADLP_par12", "EW", "BMV")])),aes(x=ind,y=values))+geom_boxplot()+labs(x="Models",y="Relative reserve bias (75th quantile)")+ggtitle("Distribution of relative reserve bias(75th quantile)")+ylim(-0.25, 0.5)+scale_x_discrete(labels = c("SLP", "ADLP 12", "EW", "BMV"), guide = guide_axis(angle = 45))

#dev.off()

```



# Analysis of optimal model weights

This section presents the results in **6.5. Analysis of optimal model weights** in the paper. 


```{r Calculation of model weights across simulations}
## Calculate the mean model weights: 

mean_weights_all <- matrix(NA, ncol = n.models, nrow = length(split_points))
for(j in 2:(length(split_points)+1)){
    model_weights_simul_mat <- matrix(NA,nrow=n.sims,ncol=n.models)
    for (i in 1:n.sims){
      model_weights_simul_mat[i,]<-as.vector(unlist(all_ensembles[[j]]$model_weights_simul_sims[[i]][1]))
    }
    mean_weights_all[j-1, ] <- apply(model_weights_simul_mat, MARGIN=2,FUN=mean)
}
## Each row represents the model weights (in subset 1) in each ADLP ensemble

## Since the weights in subset 2 is trained using all the data, all the ADLP ensembles have the same weights in Subset 2, which is equal to the weights for SLP:
model_weights_simul_mat_Subset2 <- matrix(NA,nrow=n.sims,ncol=n.models)
for (i in 1:n.sims){
      model_weights_simul_mat_Subset2[i,]<-as.vector(unlist(all_ensembles[[2]]$model_weights_simul_sims[[i]][2]))
}

mean_weights_subset2 <- apply(model_weights_simul_mat_Subset2, MARGIN=2,FUN=mean)
```


```{r Graphical Results: Estimated model weights over subsets}
##### Plotting model Weights for Subset 1: 

### Need to comment out the ZALN and ZAGA lines if one selects the triangle size to be 20: 
express <- c(
    expression(GLM[ccODP]),
    expression(GLM[ccGA]),
    expression(GLM[ccLN]),
    expression(GLM[ZAGA]),
    expression(GLM[ZALN]),
    expression(GLM[hcODP]),
    expression(GLM[hcGA]),
    expression(GLM[hcLN]),
    expression(GLM[calODP]),
    expression(GLM[calGA]),
    expression(GLM[calLN]),
    expression(SP[NO]),
    expression(SP[GA]),
    expression(SP[LN]),
    expression(GAMLSS[GA]),
    expression(GAMLSS[LN]),
    expression(GLM[ppci]),
    expression(GLM[ppcf])
)

mean_weight_ADLP_dat <- data.frame(
    Weights=c(t(mean_weights_all)), 
    Models=rep(model_names,times=length(split_points)),
    SplitPoint=rep(as.character(corres_splitpoints_SLPincluded[2:(length(split_points)+1)]),each=n.models)
)
mean_weights_ADLP<-apply(mean_weights_all, FUN=mean,MARGIN=2)
mean_weight_ADLP_dat$SplitPoint<-factor(mean_weight_ADLP_dat$SplitPoint,levels=as.character(corres_splitpoints_SLPincluded[2:(length(split_points)+1)]))

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_ModelWeightsSubset1.pdf"))
ggplot(mean_weight_ADLP_dat, aes(fill=SplitPoint, y=Weights, x=reorder(Models,-Weights))) +
    geom_bar(position="dodge", stat="identity") +
    ggtitle("Model weights under ADLP with different split points (Subset 1)") +
    labs(x="Model Names",y="Model Weights") +
    scale_x_discrete(labels=express[order(mean_weights_ADLP,decreasing=TRUE)], guide = guide_axis(angle = 45)) +
    theme(plot.margin = unit(c(0.1,0.1,0.1,0), "cm"))

#dev.off()

##### Plotting model Weights for Subset 2: 

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_ModelWeightsSubset2.pdf"))

w_M_mean<-data.frame(value=mean_weights_subset2,Models=model_names)
ggplot(data=w_M_mean,mapping=aes(x=reorder(Models,-value),y=value)) +
    geom_bar(stat="identity") +
    ggtitle("Model Weights under ADLP (Subset 2)") +
    labs(x="Model Names",y="Model Weights") +
    scale_x_discrete(labels=express[order(mean_weights_subset2,decreasing=TRUE)],guide = guide_axis(angle = 45))

#dev.off()
```

# Appendix D. Additional fitting results

This section presents the additional fitting results as shown in Appendix D in the paper. 

## Three Subset Fitting

```{r Calculating Ensemble using 3 Subset}
stopifnot(tri.size == 40)

# Note this is currently only defined for triangle size 40
all_ensembles_3par <- fit_all_partition_ensembles_40_3par(
    meta_dens_valid, 
    meta_dens_outsample
)
```

```{r Scoring Metrics over 3 subset ADLP ensemble, echo=TRUE}
ensemble_dens_3par <- calc_dens_ensemble(meta_dens_outsample, all_ensembles_3par)
ensemble_logS_3par <- lapply(
    ensemble_dens_3par, FUN = function(x) lapply(x, FUN = function(y) log(y+1e-6))
)
names(ensemble_logS_3par) <- names(all_ensembles_3par)

mean_score_over_sim_3Subsets <- lapply(ensemble_logS_3par, FUN = function(x) unlist(lapply(x, FUN = function(y) mean(y))))

```

```{r 3 Subset ADLP Log Score}
### Comparison with the 2 subsets case: 
mean_score_over_sim_2Subsets <- lapply(ensemble_logS, FUN = function(x) unlist(lapply(x, FUN = function(y) mean(y))))

mean_score_over_sim_3Subsets_new <- as.data.frame(mean_score_over_sim_3Subsets) %>%
    select(-c('ADLP_sub3_par1')) %>%
    mutate(`ADLP 9` = data.frame(mean_score_over_sim_2Subsets)[, c('ADLP_par9')],
           `ADLP 11` = data.frame(mean_score_over_sim_2Subsets)[, c('ADLP_par11')],
           `ADLP 14` = data.frame(mean_score_over_sim_2Subsets)[, c('ADLP_par14')]) %>%
    rename(`ADLP 9+` =  ADLP_sub3_par2,
           `ADLP 11+` = ADLP_sub3_par3,
           `ADLP 14+` = ADLP_sub3_par4)

mean_score_over_sim_3Subsets_new <- mean_score_over_sim_3Subsets_new[, c('ADLP 9', 'ADLP 9+',
                                                                         'ADLP 11', 'ADLP 11+',
                                                                         'ADLP 14', 'ADLP 14+')]

#pdf(paste0("plotting/triangle_", tri.size, "_", n.sims, "_LogScore3Subsets.pdf"))

ggplot(data=stack(data.frame(mean_score_over_sim_3Subsets_new)), aes(x = ind, y = values)) + 
    geom_boxplot()+labs(x="Model",y="Log Score") +
    ggtitle("Average Log Score over 100 Simulations for 3 Subset")+scale_x_discrete(labels=c('ADLP 9','ADLP 9+', 'ADLP 11', 'ADLP 11+', 'ADLP 14', 'ADLP 14+'))

#dev.off()
```

```{r ADLP Mean Log Score}
apply(mean_score_over_sim_3Subsets_new, FUN = mean, MARGIN = 2)
```

## SLP of SP_LN and GAMLSS_LS

```{r SLP of SP_LN and GAMLSS_LS}

SP_GAMLSS_LN <- fit_ensemble_model(
    lapply(meta_dens_outsample, function(x) x[, c('origin', 'dev', 'dens_SpLN', 'dens_LNGAMLSS')]),
    lapply(meta_dens_outsample, function(x) x[, c('origin', 'dev', 'dens_SpLN', 'dens_LNGAMLSS')]),
    par0
)

# SP_GAMLSS_LN$model_weights_simul_sims
```
